Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2023-10-31 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Update figures

Now, let's begin by examining the missing patterns in the data by cluster:
```{r obesity-md}
require(patchwork)
  myplots <- lapply(1:5, function(i) {
         ggmice::plot_pattern(setDT(Obesity)[Cluster==i])+ 
           ggtitle(paste0("Cluster", i))+ 
      theme(legend.position = ifelse(i==1,"bottom","none"))
      })
  myplots[[1]]+ myplots[[2]] /myplots[[3]]+ myplots[[4]] /myplots[[5]]

@@

```{r models}
library(ggplot2)
cc_rs<- with(Obesity[complete.cases(Obesity),],lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mar_rs <- with(imp_mar,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mar_pmm_rs <- with(imp_mar_pmm,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mnar_rs<- with(imp_mnar,lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mnar_pmm_rs<- with(imp_mnar_pmm, lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
list_models<-list(cc_rs,mar_rs,mar_pmm_rs,mnar_rs,mnar_pmm_rs)
plot_models(list_models,mod_name=c("Complete case", "MAR","MAR_pmm", "MNAR","MNAR_S", "MNAR_pmm"))
```

>>>>

Now, let's begin by examining the missing patterns in the data by cluster:
```{r obesity-md}
require(patchwork)
  myplots <- lapply(1:5, function(i) {
         ggmice::plot_pattern(setDT(Obesity)[Cluster==i])+ 
         ggplot2::ggtitle(paste0("Cluster", i))+ 
         ggplot2::theme(legend.position = ifelse(i==1,"bottom","none"))
      })
  myplots[[1]]+ myplots[[2]] /myplots[[3]]+ myplots[[4]] /myplots[[5]]

@@

```{r models}
library(ggplot2)
cc_rs<- with(Obesity[complete.cases(Obesity),],lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mar_rs <- with(imp_mar,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mar_pmm_rs <- with(imp_mar_pmm,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mnar_rs<- with(imp_mnar,lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
mnar_pmm_rs<- with(imp_mnar_pmm, lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
list_models<-list(cc_rs,mar_rs,mar_pmm_rs,mnar_rs,mnar_pmm_rs)
plot_models(list_models,mod_name=c("Complete case", "MAR","MAR_pmm", "MNAR", "MNAR_pmm"))
```

### 2023-10-31 Manuscript/Imputation_of_Incomplete_Multilevel_Data.tex
Update figures

\begin{CodeChunk}
\begin{CodeInput}
R> require(patchwork)
R>   myplots <- lapply(1:5, function(i) {
+          ggmice::plot_pattern(setDT(Obesity)[Cluster==i])+ 
+            ggtitle(paste0("Cluster", i))+ 
+       theme(legend.position = ifelse(i==1,"bottom","none"))
+       })
R>   myplots[[1]]+ myplots[[2]] /myplots[[3]]+ myplots[[4]] /myplots[[5]]
\end{CodeInput}

@@

    Adjusted ICC: 0.342
  Unadjusted ICC: 0.342
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mar,"long")$Weight)
\end{CodeInput}
\begin{CodeOutput}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  2.409  69.703  82.925  82.476  95.310 158.420 
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mar)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mar_pmm,"long")$Weight)
\end{CodeInput}
\begin{CodeOutput}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  27.50   71.02   83.82   83.76   95.55  135.98 
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mar_pmm)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mnar,"long")$Weight)
\end{CodeInput}
\begin{CodeOutput}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  10.26   73.41   86.94   88.27  101.73  186.47 
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mnar)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mnar_pmm,"long"))
\end{CodeInput}
\begin{CodeOutput}
      .imp           .id          Cluster           Time          Gender     
 Min.   : 1.0   Min.   :   1   Min.   :1.000   Min.   :1.016   Female:10720  
 1st Qu.: 3.0   1st Qu.: 528   1st Qu.:2.000   1st Qu.:3.724   Male  :10390  
 Median : 5.5   Median :1056   Median :3.000   Median :5.151                 
 Mean   : 5.5   Mean   :1056   Mean   :2.868   Mean   :5.211                 
 3rd Qu.: 8.0   3rd Qu.:1584   3rd Qu.:4.000   3rd Qu.:6.698                 
 Max.   :10.0   Max.   :2111   Max.   :5.000   Max.   :9.957                 
     Height      FamOb            Age            Weight            BMI       
 Min.   :1.450   no : 3794   Min.   :14.00   Min.   : 27.50   Min.   : 9.59  
 1st Qu.:1.642   yes:17316   1st Qu.:20.00   1st Qu.: 75.19   1st Qu.:25.84  
 Median :1.701               Median :25.00   Median : 88.88   Median :30.57  
 Mean   :1.702               Mean   :24.82   Mean   : 89.61   Mean   :31.02  
 3rd Qu.:1.760               3rd Qu.:29.00   3rd Qu.:103.78   3rd Qu.:35.89  
 Max.   :1.961               Max.   :47.00   Max.   :135.98   Max.   :63.21  
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mnar_pmm)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> library(ggplot2)
R> cc_rs<- with(Obesity[complete.cases(Obesity),],lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mar_rs <- with(imp_mar,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mar_pmm_rs <- with(imp_mar_pmm,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mnar_rs<- with(imp_mnar,lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mnar_pmm_rs<- with(imp_mnar_pmm, lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> list_models<-list(cc_rs,mar_rs,mar_pmm_rs,mnar_rs,mnar_pmm_rs)
R> plot_models(list_models,mod_name=c("Complete case", "MAR","MAR_pmm", "MNAR","MNAR_S", "MNAR_pmm"))
\end{CodeInput}

>>>>

\begin{CodeChunk}
\begin{CodeInput}
R> require(patchwork)
R>   myplots <- lapply(1:5, function(i) {
+          ggmice::plot_pattern(setDT(Obesity)[Cluster==i])+ 
+          ggplot2::ggtitle(paste0("Cluster", i))+ 
+          ggplot2::theme(legend.position = ifelse(i==1,"bottom","none"))
+       })
R>   myplots[[1]]+ myplots[[2]] /myplots[[3]]+ myplots[[4]] /myplots[[5]]
\end{CodeInput}

@@

    Adjusted ICC: 0.362
  Unadjusted ICC: 0.362
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mar,"long")$Weight)
\end{CodeInput}
\begin{CodeOutput}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 -19.48   68.45   81.65   81.28   94.12  160.76 
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mar)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mar_pmm,"long")$Weight)
\end{CodeInput}
\begin{CodeOutput}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  28.35   69.55   82.54   82.47   94.83  134.61 
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mar_pmm)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mnar,"long")$Weight)
\end{CodeInput}
\begin{CodeOutput}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
 -0.3457  71.4561  84.9177  85.1453  98.5923 182.3955 
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mnar)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> summary(complete(imp_mnar_pmm,"long"))
\end{CodeInput}
\begin{CodeOutput}
      .imp           .id          Cluster           Time          Gender     
 Min.   : 1.0   Min.   :   1   Min.   :1.000   Min.   :1.016   Female:10720  
 1st Qu.: 3.0   1st Qu.: 528   1st Qu.:2.000   1st Qu.:3.724   Male  :10390  
 Median : 5.5   Median :1056   Median :3.000   Median :5.151                 
 Mean   : 5.5   Mean   :1056   Mean   :2.868   Mean   :5.211                 
 3rd Qu.: 8.0   3rd Qu.:1584   3rd Qu.:4.000   3rd Qu.:6.698                 
 Max.   :10.0   Max.   :2111   Max.   :5.000   Max.   :9.957                 
     Height      FamOb            Age            Weight            BMI        
 Min.   :1.450   no : 3954   Min.   :14.00   Min.   : 28.35   Min.   : 8.191  
 1st Qu.:1.642   yes:17156   1st Qu.:21.00   1st Qu.: 71.74   1st Qu.:24.699  
 Median :1.701               Median :25.00   Median : 85.36   Median :29.396  
 Mean   :1.702               Mean   :24.88   Mean   : 85.99   Mean   :29.717  
 3rd Qu.:1.761               3rd Qu.:29.00   3rd Qu.: 99.26   3rd Qu.:34.216  
 Max.   :2.012               Max.   :47.00   Max.   :134.61   Max.   :61.911  
\end{CodeOutput}
\begin{CodeInput}
R> plot(imp_mnar_pmm)
\end{CodeInput}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> library(ggplot2)
R> cc_rs<- with(Obesity[complete.cases(Obesity),],lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mar_rs <- with(imp_mar,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mar_pmm_rs <- with(imp_mar_pmm,lme( BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mnar_rs<- with(imp_mnar,lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> mnar_pmm_rs<- with(imp_mnar_pmm, lme(BMI ~ Age + FamOb + Gender,random=~1+Age|Cluster))
R> list_models<-list(cc_rs,mar_rs,mar_pmm_rs,mnar_rs,mnar_pmm_rs)
R> plot_models(list_models,mod_name=c("Complete case", "MAR","MAR_pmm", "MNAR", "MNAR_pmm"))
\end{CodeInput}
